---
title: "Filter/joins (like LOOKUP in Excel)"
author: "Molly Troup"
date: "December 8, 2019"
output: html_document
---

##Attach packages
tidyverse, readxl, here

```{r, include = FALSE}
library(tidyverse)
library(readxl)
library(here)
```

Read in 3 files:
- invert_counts_curated.xlxs
- fish_counts_curated.csv
- kelp_countscurated.xlxs

```{r}
invert_counts <- read_excel(here("R-workshop-data", "invert_counts_curated.xlsx"))
  

fish_counts <- read_csv(here("R-workshop-data", "fish_counts_curated.csv"))

  
kelp_counts_abur <- read_excel(here("R-workshop-data", "kelp_counts_curated.xlsx"))   
  
```

## Select () function: keep, exclude or rearragnge columns
-filter() function: keeps or excludes



```{r}
fish_garibaldi <- fish_counts %>%
  filter(common_name == "garibaldi")
```
### use janitor:: clean_names() to autoatically update all of your column naes to lowerse_snake_case

## Filter to keep/exclude observations based on numeric conditions

create a subset where total_counts is grewat than or equal to 50:

```{r}
fish_over50 <- fish_counts %>%
  filter(total_count >=50)
```

Create a subset that only contians observations for fish at Mokawk Reef ("mohk")

```{r}
mohawk_fish <- fish_counts %>%
  filter(site == "mohk")
```

##Filter to keep rows that match THIS or THAT

Example: we want to keep any observations for garibaldi, blacksmith, or black surfperch


Use the %in% operator to look for any matches within a vector
```{r}
fish_3sp <- fish_counts %>%
  filter(common_name %in% c("garibaldi", "blacksmith", "black surfperch"))
#Writing OR statements explicityly:
#use veritical line | to indicate "or"
fish_3sp_v2 <- fish_counts %>%
  filter(common_name == "garibalide" | common_name == "blacksmith" | common_name =="black surfperch")
```

## Filter to return rows that match conditions for multiple variables (AND statements)

I want to create a subset called urchin_abur_mohk that only keeps observations where: 
-site is "abur" or "mohk" AND
-species is "purple urchin"

some ways to do this: 
- sepearate "AND" conditions within a single filter line by a comma
- separate "AND" conidtions within a single filter line by an ampersand (&)
- putting each filger condition within a separate filter line

Reminder: "OR" %in%
```{r}
urchin_abur_mohk <- invert_counts %>%
  filter(site %in% c("abur", "mohk"), common_name == "purple urchin")
```


