---
title: "intro-to-ggplot2"
author: "Molly Troup"
date: December 8, 2019
output: html_document
---
## Attach packages


```{r}
library (tidyverse)
library(readxl)
library(here)

```

### Read in the data

```{r}
ca_np <- read_csv(here("R-workshop-data", "ca_np.csv"))
ci_np <- read_xlsx(here("R-workshop-data", "ci_np.xlsx"))

```
## Make a graph
1. Tell R we're using "`gglot`"
2. Tell R what data we're using and what variables we want to plot
3. What type of graph we're creating (geom)

```{r, eval = FALSE}
ggplot(data = This. aes(x = THIS, y=THIS)) +
  geom_THIS()

#Now let's create a graph of CI visitation:


```

```{r}
ggplot(data = ci_np, aes(x= year, y = visitors)) +
  geom_line()
```

1. Create a column graph with this data
2. Create an area graph with this data


```{r}
ggplot(data = ci_np, aes(x= year, y = visitors)) +
  geom_col()
```

```{r}
ggplot(data = ci_np, aes(x= year, y = visitors)) +
  geom_area()
```


## Intro to customizing `ggplot` graphs

- color = (to update point or line colors)
- fill = (update the fill characteristic of an element)
- linetype =
- pch = (value)
- size = 
- alpha = 

```{r}
ggplot(data=ci_np, aes(x= year, y = visitors)) +
  geom_line(color="coral4", linetype="solid")
```

```{r}
ggplot(data=ci_np, aes(x= year, y = visitors)) +
  geom_point(color = "blue",
             pch = 17,
             sixe = 4, 
             alpha = 0.5)
```

```{r, echo = FALSE}
ggplot(data=ci_np, aes(x= year, y = visitors)) +
  geom_area(color = "yellow",
             pch = 10,
             sixe = 10, 
             alpha = 0.8)
```

I have some awesome text here, and below is my amazing finalized graph: 

## Customize elements based on variables or outcomes

```{r}

ggplot(data = ci_np, aes(x= year, y= visitors)) +
  geom_point(aes(size = visitors,
                 color = visitors), 
             pch = 17, 
             alpha = 0.5)


```

Activity: create a column plot of CINP visitation over time, where the FILL COLOR changes based on the number of visitors, and the outline color (color =) is "magenta"

```{r}
ggplot(data = ci_np, aes(x= year, y = visitors)) +
  geom_col(aes(fill= visitors), 
           color = magenta)
```

```{r}

```
## Add/update labels and titles

Using `labs`
```{r}
ggplot(data = ci_np, aes(x= year, y=visitors))+
  geom_point((size= 1,
              color= "navy") +
               theme_minimal()+
               labs(x="My x-axis title", 
                    y= "Annual Visitors",
                    Title = "Channel Islands NP Visitation",
                    submititle = "1963-2016"
                  
```


### Combine compatible geoms

```{r}
ggplot(data = ci_np, aes(x=year, y=visitors))+
  geom_line (color = "purple" +
  geom_point(color = "magenta", 
              aes(size= year))
```


Create a combined column graph + line graph of visitation

```{r}
ggplot(data= ci_np, aes(x = year, y=visitors)) +
  
```


## Create a line graph with mulitple series

```{r}
ggplot(data = ca_np, aes(x = year, y = visitors, color = park_name)) +
  geom_line()
```

### Faciting ggplot graphs
- each series gets it's own plot panal

```{r}
ggplot(data = ca_np, aes(x = year, y = visitors, color = park_name)) +
  geom_line(show.legend = FALSE) + 
  theme_minimal() +
  facet_wrap(~ park_name)
```




### Use ggsave to export a plot

```{r}
ggsave("np_graph.png", dpi = 180, width = 8, height = 7)
```


