---
title: "Intro readxl"
author: "Molly Troup"
date: "Decenber 7,2019"
output: html_document
---

# Learning 'readxl'

We are working with data in readxl and it's going to be amazing!

We're giong to use the following packages:

- tideyverse
- readxl
- writexl
- here



```{r packages}
library(tidyverse)
library(readxl)
library(writexl)
library(here)

### Read in fish counts



```

# install.packages ("package_name")
```{r}
  #### read in the fish_counts_curated.csv
fish_counts <-read_csv(here("R-workshop-data", "fish_counts_curated.csv"))

#fish_counts <-read_csv ("R-workshop-data/fish_counts_curaged.csv")

```
#### Read in data from a single Excel Worksheet

now to read in an excel spreadsheet, we'll use the function 'read_excel()'

```{r}
substrate_cover <-read_excel(here("R-workshop-data", "substrate_cover_curated.xlsx") , 
                             skip = 4, 
                             na = "-9999")
```
#### Use read_excel() to read in a range of values 
```{r}
carp_cover_2000 <-read_excel(here("R-workshop-data", "substrate_cover_curated.xlsx"), range ="D12:I15", col_names = c("site", "transect","quad", "side", "type", "coverage"))

```
### How can we read in data from an Excel workbook with Multiple worksheets?

```{r}

```











