---
title: "Pivot Tables"
output: html_document
---
## Attach libraries

```{r}
library(tidyverse)
library(readxl)
library(here)
library(skimr) #install.packages("skimr")
```

## Read in our data about lobsters

```{r}
lobsters <- read_xlsx(here("R-workshop-data/lobsters2.xlsx"))

#head() function show the first 6 lines of data
## skimr:: skim() gives additional summary statistics and is pipable (%>%)

skim(lobsters)
```

##ggplot of lobsters
```{r}
ggplot(data = lobsters, aes(x=year)) +
geom_bar() +
facet_wrap(~site)
```



##our task:
how has the ave size of lobsters has changed overtime accross sites?

Pivot tables in R are group_by %>% summarize


```{r}
lobsters%>%
  group_by(year)%>%
  summarise(count_by_year = n())
```

What if we didnt' group_by first?

```{r}
lobsters %>%
  summarize(count_by_something = n())
```
## assign our summary to a new variable

lobsters_sum <- lobsters%>%
  summarize(count_by_comething = n())
  
## group by muliple variables and summarize by multiple variables
We used mean() to calculate the mean size of lobsters by each site and year, and used na.rm = TRUE to calculate mean despite having missing values in our raw data


```{r}
siteyear_summary <- lobsters %>%
  group_by(site, year) %>%
  summarise(count_by_siteyear = n(),
            mean_size_mm = mean(size_mm, na.rm = TRUE),
            sd_size_mm = sd(size_mm, na.rm = TRUE),
            median_size_mm = median(size_mm, na.rm = TRUE))
siteyear_summary

##ggplot: geom_line

ggplot(data = siteyear_summary, aes(x = year, y = median_size_mm, color = site)) +
  geom_line()

## I created a figures folder from the Rstudio Files pane in order to be organized and for this code to run:
ggsave(here("figures/lobsters-line.png"))
```

## Activity
1. Calculate the meadian size_mm (?median)
2. Create and ggsave() a plot

# dplyr::count() for counting by group
This is a "shortcut function

```{r}
lobsters%>%
  count(site, year)

## This is the same  as

lobsters %>%
  group_by(site, year) %>%
  summarize(n = n()) %>%
  ungroup ()

```

# mutate() add a new column
it will make a new variable

- Add a new column that is the size in meters
- Add a new column that is a repeated value
```{r}
head(lobsters)

lobsters %>%
  mutate(size_m = size_mm / 1000, 
         millenia = 2000, 
         observer = "Allison Horst")

```

## Use select() function to subset variables by columns
lets select 
- date
- site
- size_m

```{r}
lobsters_selected <- lobsters %>%
  mutate(size_m = size_mm / 1000) %>%
  select(date, site, size_m)
```


